### 2016-12-05 src/group-2-approximation.tex
first draft

\begin{remark}
Clearly, if the weights on the edges are integral and polynomial bounded the
algorithm runs in polynomial time, this is because in each iteration the
algorithm improves the value of the matching by at least one or otherwise it
terminates.
\end{remark}

@@

\begin{remark}
Determining if a vertex $v$ can be improved can be done efficiently
by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
and only ones with positive value.
Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
sum up to more than $val_M(v)$.
\end{remark}

@@

\begin{theorem}
Algorithm~\ref{alg:grd} is 2-approximation.
\end{theorem}

@@

>>>>

\begin{remark}
\label{rem:improve}
Determining if a vertex $v$ can be improved can be done efficiently
by considering the incoming arcs to $v$ in a decreasing order of their $\delta$s,
and only ones with positive value.
Vertex $v$ can be improved, then, if the $\delta$s of the first $c(v)$ (or less) arcs
sum up to more than $val_M(v)$.
\end{remark}

\begin{remark}
It is easy to see, if the weights on the edges are integral and polynomial
bounded the algorithm runs in polynomial time, this is because in each iteration the
algorithm improves the value of the matching by at least one or otherwise it
terminates.
\end{remark}

@@

@@

\begin{theorem}
Algorithm~\ref{alg:grd} is $\frac{1}{2}$-approximation.
\end{theorem}

@@

We now argue that this algorithm can be generalized to solve the group carpool
matching problem.
The main concern when trying to adopt the algorithm to the group carpool
matching is how to determine if a vertex can be improved.
Observe that Remark~\ref{rem:improve} does not hold anymore.
If the maximum possible capacity is bounded, one can test for improvement of
$v$ by considering all the subsets of edges intersecting $v$. 
When the capacity is unbounded, however, it is easy to see that efficient
way to test improvement implies a solution to the Knapsack problem.
Indeed, if this is the case, one can test for improvement by using a known FPTAS
for Knapsack, this is in the cost of additional $\varepsilon$ reduction in the
approximation ratio of the algorithm.
